Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-04-01 paper/src/paper.tex
changes to expe section.

  \label{fig:mosn}
\end{figure*}

@@

The selection of a policy is of course reminiscent of reinforcement learning.
It is important to note, however, that a pure reinforcement learning approach
is difficult to develop in our context. Indeed, while we have outlined a
reduced action space, the state space to consider is infinite. This is not
prohibitive \textit{per se}, as modern methods~\ref{approximatereinforcement}
can bypass dimensionality issues via function approximation. However, these
methods rely on large amounts of data, and we are studying online (often called
\textit{on-policy} methods in reinforcement learning) methods. We rely here on
simpler, yet we believe more effective, strategies to solve this problem.
These strategies are applied online and rely on exact simulation, noisy
simulation and $\epsilon$-greedy bandit exploration.

@@

%\begin{algorithm}[h]
%  \caption{Epsilon-Greedy Bandit policy}
%  \begin{algorithmic}[1]
%    \renewcommand{\algorithmicrequire}{\textbf{Input:}}
%    \renewcommand{\algorithmicensure}{\textbf{Output:}}
%    \REQUIRE $0 < \epsilon < 1$, $K>1$
%    \FOR {$t = 1, 2, \ldots$}
%    \STATE Let $i_t$ be the reordering heuristic with the highest current
%    average reward.
%    \STATE With probability $1-\epsilon$ use $i_t$ and with probability
%    $\epsilon$ use a random reordering heuristic.
%    \ENDFOR
%  \end{algorithmic}
%  \label{alg:epsg}
%\end{algorithm}

@@

\begin{itemize}
  \item All fixed $P_i$ for $1<i<10$.
  \item The simulation-based ("full feedback") strategy.
  \item The noisy simulation ("noisy feedback") variant.
  \item The bandit feedback strategy with a fixed value of $\lambda=0$.
\end{itemize}

This campaign of 7 (traces) * 100 (resampling) * 13 Policies

@@

\begin{figure*}[h]
  \centering
  \includegraphics[scale=0.6]{figures/CTC-SP2.pdf}
  \includegraphics[scale=0.6]{figures/KTH-SP2.pdf}\\
  \includegraphics[scale=0.6]{figures/CEA-Curi.pdf}
  \includegraphics[scale=0.6]{figures/SDSC-BLU.pdf}\\
  \includegraphics[scale=0.6]{figures/SDSC-SP2.pdf}
  \includegraphics[scale=0.6]{figures/ANL-Intr.pdf}

>>>>

  \label{fig:variability}
\end{figure*}

@@

The selection of a policy is of course reminiscent of reinforcement learning.
It is important to note, however, that a pure reinforcement learning approach
is difficult to develop in our context. Indeed, while we have outlined a
reduced action space, the state space to consider is infinite. This is not
prohibitive \textit{per se}, as modern methods~\cite{aprl}
can bypass dimensionality issues via function approximation. However, these
methods rely on large amounts of data, and we are studying online (often called
\textit{on-policy} methods in reinforcement learning) methods. We rely here on
simpler, yet we believe more effective, strategies to solve this problem.
These strategies are applied online and rely on exact simulation, noisy
simulation and $\epsilon$-greedy bandit exploration.

@@

@@

\begin{itemize}
  \item All fixed $P_i$ for $1<i<10$.
  \item The simulation-based ("full feedback") strategy.
  \item The noisy simulation ("noisy feedback") variant.
  \item The bandit feedback strategy with hyperparameters $\lambda=0$, $\Delta=1 \text{day}$
  \item The bandit feedback strategy with hyperparameters $\lambda=0$, $\Delta=1 \text{week}$.
\end{itemize}

This campaign of 7 traces * 100 resampling * 13 algorithms is repeated

@@

\begin{figure*}[ht]
  \centering
  \includegraphics[scale=0.6]{figures/CTC-SP2.pdf}
  \includegraphics[scale=0.6]{figures/KTH-SP2.pdf}\\
  \includegraphics[scale=0.6]{figures/CEA-Curi.pdf}
  \includegraphics[scale=0.6]{figures/SDSC-BLU.pdf}\\
  \includegraphics[scale=0.6]{figures/SDSC-SP2.pdf}
  \includegraphics[scale=0.6]{figures/ANL-Intr.pdf}
